### 2022-11-15 paper-thesis/chapters/30-comparing-with-haskell.tex
Some writing

@@

>>>>

Finally, we define the two functions \verb|sPutSubst| and \verb|sPutType| to mimic the Statix relations with the same name.
\begin{lstlisting}
sPutSubst :: Env -> SExpr -> Env
sPutSubst env v = NSubst v : env
sPutType :: Env -> Expr -> Env
sPutType env v = NType v : env
\end{lstlisting}

@@

In Haskell, a slightly different structure was used. We defined two functions, one returning a \verb|Maybe SExpr| and the other checking if the result \verb|Nothing|, in which case it returns the original expression (unreduced). This structure could also be implemented in Statix, but Haskell makes it a bit easier for us by providing the \verb|Maybe| type and functions on it.
\begin{lstlisting}
brh :: SExpr -> SExpr
brh e = fromMaybe e (brh_ e [])
brh_ :: SExpr -> [SExpr] -> Maybe SExpr
\end{lstlisting}
